---
title: "Checking multiple models"
author: "CJ Brown"
date: "16 February 2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Checking multiple models}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, fig.width = 8)
```

### Simulate some data 

```{r}
n <- 50
a <- 1
beta <- cbind(1,2)
x <- rbind(runif(n), runif(n))
linpred <- a + beta %*% x
dat <- data.frame(x1 = x[1,],
                  x2 = x[2,], 
                  y = rpois(n, exp(linpred)))
```


### Fit a GLM


```{r}
library(visreg)

m1 <- glm(y ~ x1 + x2, data = dat, 
           family = "poisson")

visreg(m1, scale = "response")

```

### Check DS residuals 

"Dunn-Smyth" residuals ([AKA randomized quantile residuals]{https://www.jstor.org/stable/1390802?seq=1#metadata_info_tab_contents}) are useful for non-Gaussian GLMs. 

```{r}
library(DataGLMRepeat)

dat <- dplyr::bind_cols(dat, data.frame(Estimate = predict(m1, type = "response")))
m1_resids <- with(dat, ds_resids(y, Estimate, family = "poisson"))
```

## Fit multiple models based on a dataframe 

Here we fit four different models with different combinations of model formulas and priors. 

The trick here is to avoid factors in the input dataframe (i.e. `dfsim`) and to make sure data goes in and out of the expression in the right form. Note we convert each `m1` to a list object so we can bind it as a cell in a tibble. 

```{r}
library(dplyr)
dfsim <- expand.grid(form = c("y ~ x1", "y ~ x1 + x2"), 
                     family = c("poisson", "quasipoisson"), 
                     stringsAsFactors = FALSE) %>% 
  mutate(ID = 1:n()) %>%
  as_tibble()

dout <- dfsim %>%
  group_by(ID) %>%
  with_groups({
    m1 <- glm(formula(form),
              family = family,
              data = dat)
    tibble(model = list(m1))
  }) %>%
  bind_rows(.id = "groups") %>%
  bind_cols(dfsim, .)
```

### Check residuals for models 

Checking DS residuals. Notice how observations with high `x2` are grouped when `x2` is missing from the formula: 

```{r}
library(ggplot2)
gout <- dout %>%
  group_by(ID) %>%
  with_groups({
    p <- bind_cols(dat, 
                data.frame(Estimate = predict(model[[1]], type = "response")))
    p$ds <- ds_resids(dat$y, p$Estimate, plotds = FALSE, 
              family = "poisson")
    g1 <- ggplot(p) + 
      aes(x = Estimate, y = ds, color = x2) + 
      geom_point() + 
      ggtitle(paste_(form, family))
    list(g1)
  })
gout[[3]]
```

The most painful thing setting this up is getting the data structures right.


### Find 'best' model 

```{r}
library(purrr)
daic <- dout$model %>% 
  map(~AIC(.x)) %>%
  unlist()
dfsim[which.min(daic),]
```

Which is the model that generated the data. Note that there is no AIC defined for the `quasipoison` GLM. 



### Fit a Bayesian GLM

The below examples aren't run (to save time in compiling the pkg), but they are just the brms version of above. 


```{r eval=FALSE}
library(brms)
library(patchwork)

m1 <- brm(y ~ x1 + x2, data = dat, 
           family = "poisson")

ce <- conditional_effects(m1)

plot(ce, plot = FALSE)[[1]] | plot(ce, plot = FALSE)[[2]]

```

### Check DS residuals 

```{r eval=FALSE}
dat <- dplyr::bind_cols(dat, data.frame(predict(m1)))
m1_resids <- with(dat, ds_resids(y, Estimate, family = "poisson"))
```

### Fit multiple models based on a dataframe 

Here we fit four different models with different combinations of model formulas and priors. 

The trick here is to avoid factors in the input dataframe (i.e. `dfsim`) and to make sure data goes in and out of the expression in the right form. Note we convert each `m1` to a list object so we can bind it as a cell in a tibble. 

```{r  eval=FALSE}
dfsim <- expand.grid(form = c("y ~ x1", "y ~ x1 + x2"), 
                     prior = c("normal(0, 0.1)", "normal(0, 10)"), 
                     stringsAsFactors = FALSE) %>% 
  mutate(ID = 1:n()) %>%
  as_tibble()

dout <- dfsim %>%
  group_by(ID) %>%
  with_groups({
    m1 <- brm(formula(form),
              family = "poisson",
              prior = set_prior(prior),
              data = dat)
    
    tibble(model = list(m1))
  }) %>%
  bind_rows(.id = "groups") %>%
  bind_cols(dfsim, .)
```

### Check residuals for models 

Checking DS residuals. Notice how observations with high `x2` are grouped when `x2` is missing from the formula: 

```{r  eval=FALSE}
gout <- dout %>%
  group_by(ID) %>%
  with_groups({
    p <- bind_cols(dat, 
                data.frame(predict(model[[1]])))
    p$ds <- ds_resids(dat$y, p$Estimate, plotds = FALSE, 
              family = "poisson")
    g1 <- ggplot(p) + 
      aes(x = Estimate, y = ds, color = x2) + 
      geom_point() + 
      ggtitle(paste_(form, prior))
    list(g1)
  })
gout[[3]]
```

The most painful thing setting this up is getting the data structures right. e.g. brms functions output everything as matrices, we usually want them as data frames though. 


### Find 'best' model 

```{r  eval=FALSE}
dloo <- dout$model %>% 
  map(~loo(.x)$estimate[3,1]) %>%
  unlist()
dfsim[which.min(dloo),]
```

Which chooses the model that generated the data. 



